Think deep for reef resilience

### 2025-07-05 paper/paper_draft.qmd
Remove unneeded information from 'relative' coral cover analyses

Tropical cyclones and impact of wave activity to reefs are not included in this investigation. We scale coral bleaching impacts by a coefficient determined by the median depth of each reef location, following Baird et al. [@baird2018], reducing the proportion of coral colonies on a reef impacted by high heat stress as depth increases. Median depths for each reef location have been extracted from satellite derived bathymetry data for the Great Barrier Reef (GBRMPA [-@gbr10gb2020]) (see discussion for more details). Due to varying degrees of alignment between bathymetry data and the defined outlines for GBR reefs, reefs with less than 5% coverage of valid bathymetry data have been removed from this investigation. Furthermore, reefs that were outside the GBRMPA management areas or not associated with a bioregion were removed from the investigation, as well as reefs with relative coral cover values greater than five [**five what???**].

@@

Each GCM shows similar relationships between reefs in clusters of ‘low’, ‘medium’ and ‘high’ coral cover and contextual analysis factors, thus visual further comparisons of these clusters for each analysis factor are only shown for ACCESS-ESM1-5 GCM (intermediate ECS scenario). Results for the additional GCMs are displayed in the supplementary material. However, there are substantial differences in the longevity of reef resilience and maintenance of coral cover post 2030 between the GCMs, thus relative coral cover timeseries are displayed for each GCM (displayed at management-area scale to preserve coarse spatial differences in coral trajectories) (@fig-gcm-cover-trajectories).

>>>>

Tropical cyclones and impact of wave activity to reefs are not included in this investigation. We scale coral bleaching impacts by a coefficient determined by the median depth of each reef location, following Baird et al. [@baird2018], reducing the proportion of coral colonies on a reef impacted by high heat stress as depth increases. Median depths for each reef location have been extracted from satellite derived bathymetry data for the Great Barrier Reef (GBRMPA [-@gbr10gb2020]) (see discussion for more details). Due to varying degrees of alignment between bathymetry data and the defined outlines for GBR reefs, reefs with less than 5% coverage of valid bathymetry data have been removed from this investigation. Furthermore, reefs that were outside the GBRMPA management areas or not associated with a bioregion were removed from the investigation.

@@

Each GCM shows similar relationships between reefs in clusters of ‘low’, ‘medium’ and ‘high’ coral cover and contextual analysis factors, thus visual further comparisons of these clusters for each analysis factor are only shown for ACCESS-ESM1-5 GCM (intermediate ECS scenario). Results for the additional GCMs are displayed in the supplementary material. However, there are substantial differences in the longevity of reef resilience and maintenance of coral cover post 2030 between the GCMs, thus coral cover timeseries are displayed for each GCM (displayed at management-area scale to preserve coarse spatial differences in coral trajectories) (@fig-gcm-cover-trajectories).
